\speculake: Hiding Malware in Speculative Execution

### 2018-12-14 paper/introduction.tex
small gramatical patch

% Results summary
In order to study the potential of \speculake, we implement several example
payload programs and triggers variants, and evaluate their performance. We find
that the payload program's speculative
window is mainly limited by the CPU's reorder buffer, which
allows us to execute up to 200 instructions speculatively on modern
Intel CPUs. While brief, we show how to perform execution in short steps,
communicating intermediate results back to the ``real world'' part of the
payload program. Using this technique, we demonstrate implementing a universal
Turing machine (demonstrating arbitrary computation), a custom instruction set
architecture that fits within the constraints of speculative execution, and show
the ability to perform AES decryption using AES-NI instructions.

>>>>

% Results summary
In order to study the potential of \speculake, we implement several example
payload programs and trigger variants, and evaluate their performance. We find
that a payload program's speculative
window is mainly limited by the CPU's reorder buffer, which
allows us to execute up to 200 instructions speculatively on modern
Intel CPUs. While brief, we show how to perform execution in short steps,
communicating intermediate results back to the ``real world'' part of the
payload program. Using this technique, we demonstrate implementing a universal
Turing machine (demonstrating arbitrary computation), a custom instruction set
architecture that fits within the constraints of speculative execution, and show
the ability to perform AES decryption using AES-NI instructions.
